Invariant Representations for Noisy Speech Recognition

### 2016-10-23 paper.tex
Discuss future work

\begin{figure}
    \centering
    \captionsetup[subfigure]{oneside,margin={0.3cm,0cm}}
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=0.9\linewidth]{model.pdf}
        \caption{The model consists of three neural networks. The encoder $E$ produces
        the intermediate representation $h$ which used in the recognizer $R$ and 
        in the discriminator $D$. The hidden representation $h$ is trained to improve
        the recognition and minimize the discrimination accuracy. The discriminator
        is a classifier trained to maximize its accuracy on the gender or the noise type
        recognition task.}
        \label{fig:model}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{wer_avg.pdf}
        \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
        \caption{Up: Average performance of the model depending on the number of noise
            conditions used for training. Bottom: Average performance on seen condition versus unseen.
            Testing was performed on all wv1 conditions.
            }
        \label{fig:results}
    \end{subfigure}
    \caption{Model and results.}
\end{figure}

@@

In order to evaluate the impact of our method on generalization to new, unseen noises 
we performs 6 groups of experiments with different set of seen noises. We always train
on clean data and add noise conditions one-by-one in order: airport, babble, car, 
restaurant, street, train. The last group includes all noises therefore matches the
standard multi condition training setup. For every group of experiments we trained the
baseline and the invariance model where we branch out at 4th layer to a logistic 
binary classifier clean versus noisy data. Due to the imballance between clean and
noisy parts of the dataset, we had to oversample noisy frames, every minibatch contained
half of clean and half of noisy data points.

@@

\section{Discussion}
    We demonstrate that the invariance training helps to generalize to unseen noise
    conditions and improves in

>>>>

\begin{figure}
    \centering
    \captionsetup[subfigure]{oneside,margin={0.3cm,0cm}}
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=0.9\linewidth]{model.pdf}
        \caption{The model consists of three neural networks. The encoder $E$ produces
        the intermediate representation $h$ which used in the recognizer $R$ and 
        in the discriminator $D$. The hidden representation $h$ is trained to improve
        the recognition and minimize the discrimination accuracy. The discriminator
        is a classifier trained to maximize its accuracy on the gender or the noise type
        recognition task.}
        \label{fig:model}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{wer_avg.pdf}
        \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
        \caption{Up: Average performance of the model depending on the number of noise
            conditions used for training. Bottom: Average performance on seen condition versus unseen.
            Testing was performed on all wv1 conditions.
            }
        \label{fig:results}
    \end{subfigure}
    \caption{Model structure and results.}
\end{figure}

@@

In order to evaluate the impact of our method on generalization to new, unseen noises 
we performs 6 groups of experiments with different set of seen noises. We always train
on clean data and add noise conditions one-by-one in order: airport, babble, car, 
restaurant, street, train. The last group includes all noises therefore matches the
standard multi condition training setup. For every group of experiments we trained the
baseline and the invariance model where we branch out at 4th layer to an  
binary classifier clean versus noisy data. Due to the imballance between clean and
noisy parts of the dataset, we had to oversample noisy frames, every minibatch contained
half of clean and half of noisy data points.

@@

\section{Discussion}
    We demonstrate that the invariance training helps to generalize to unseen noise
    conditions and improves in the case of a small amount of training noise. Future
    research on this topic includes experimentation with layerwise pretraining,
    more architecture exploration, and the form of the invariance promotion cost term.
